---
title: "Analysis"
author: "Mihai Vlad Serbanescu"
date: "21/03/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Motivation

In 2017, a research review paper by Agnieszka Lisowska brought together several research experiments done on the subject of crime in tourism destination. Liowska (2017) believed this subject important as the large growth of the tourism industry world-wide is unevenly matched to a small amount of studies that observe this matter within urban tourist areas. Conceptually, she argues a logical relation between tourism and crime, as tourism leads to an increase inflow of strangers to unknown communities, thus increasing the risk of crime either done by or to tourists. It is concluded that while research on the negative aspects of tourism (such as impacts on nature, social or cultural environments) does exist, there is insufficient research on how criminalistic statistics are related to this phenomenon (Lisowska, 2017).
A research paper done by Ke, O’Brien & Heydari (2021) aims to contribute to this issue by observing how Airbnb listings might enable or generate crime specifically in the city of Boston, United States. The usage of Airbnb is rather innovative and also logical, as Airbnb has become a major industry leader among hosting platforms as it has raised in value exponentially – being valued at $113 billion in 2021 (Lock, 2022). The research categorizes crime as private conflict, public social disorder, and violence. Ultimately, the research suggests that Airbnb presence in a neighbourhood is significantly correlated only with increased violence. A concluding argument is that tourism may not have an effect on crime, rather the conversion of housing into short-term rental property  undermines a neighbourhood’s social organization, thus leading to increased crime (Ke, O’Brien & Heydari, 2021).

Having observed these research papers, this team is intrigued in conducting a similar analysis and further contributing to this field. The following research question is examined:

*To what extent does the number of Airbnb listings affect crime rates within Amsterdam, and to what extent is this relationship different within different Amsterdam neighborhoods.*

A major change is that this research will focus on the city and neighborhoods of Amsterdam, Netherlands, rather than Boston. This enables us to investigate whether the results are replicable or applicable for a different geographical location whilst contributing to a field lacking research. Naturally, available datasets are different between international geographical locations, which primarily implies that crime categorization will be different compared to previous research. Furthermore, it is transparent to note that some aspects of the analysis will be simplified – this will not only allow the team to conduct these analyses at their own level, but also account for other data absences not present in previous research. 

The team believes this research is relevant on multiple levels. The academic benefits of this research extend beyond replication at different geographical parameters and contribution to a field that lacks research – it may enable a method of analyzing this phenomenon with more internationally readily available data. From a social perspective, this research can be particularly informative to homeowners (or prospective homeowners) who would like to stay informed on how services alike to Airbnb affect the neighborhood they live or would like to live in. Furthermore, this research can be of importance to policymakers (Ke, O’Brien & Heydari, 2021) and enforcement stakeholders (security businesses, police departments etc.), as it provides correlational evidence to whether Airbnb listings do or do not affect crime rates, and if they do, what changes can they expect so that security planning can be adjusted. Lastly, this research can be of relevance to Airbnb (as well as similar businesses), as it allows them to account for changes in local environments they might enable, but are not be fully aware of. This is particularly important to Airbnb, as its previous enablement of pollution in Japan had cost the company $10 million in compensation(McCurry, 2018) – there is always a possibility that another government may also do the same on the front of criminality enablement. Other possible stakeholders include hotels that rent to Airbnb users and tourism agencies that use/are partnered with Airbnb. It will enable them to stay informed of the changes in local environment caused by Airbnb and allow them to predict possible shortcomings or dangers.  


## Exploratory Analysis

```{r, data-load, echo=FALSE}

listings_crime_dataset <-read.csv("../../temp-data/analysis/listings_crime_dataset.csv")

```

```{r, library-load, echo=FALSE, include=FALSE}
#Load all libraries we need here, in one code chunk even if they are used in different sections
library(dplyr)
library(ggplot2)
library(tidyverse)
library(broom)
```

```{r, descriptives, echo=FALSE, include=FALSE}
x = nrow(listings_crime_dataset)
x_neigh = nrow(listings_crime_dataset %>%group_by(neighborhood) %>% summarise(count=n()))
x_period = nrow(listings_crime_dataset %>%group_by(periods) %>% summarise(count=n()))
df_listings = listings_crime_dataset %>% group_by(neighborhood) %>% summarise(total_listings = sum(listing_sum))
df_max_listings = df_listings[which.max(df_listings$total_listings),]
n_m_l = df_max_listings[1,1]
n_m_l_n = df_max_listings[1,2]
df_min_listings = df_listings[which.min(df_listings$total_listings),]
n_l_l = df_min_listings[1,1]
n_l_l_n = df_min_listings[1,2]
df_price = listings_crime_dataset %>% group_by(neighborhood) %>% summarise(average_price)
df_max_price = df_price[which.max(df_price$average_price),]
n_m_p = df_max_price[1,1]
n_m_p_n = df_max_price[1,2]
df_min_price = df_price[which.min(df_price$average_price),]
n_l_p = df_min_price[1,1]
n_l_p_n = df_min_price[1,2]
```
To begin this analysis, this report will first highlight some descriptive statistics about the dataset used. To begin with, the dataset contains `r x` rows worth of data, with each row highlighting the amount of listings and crimes (per type), the average listings price, and percentages per listing types based on an Amsterdam neighborhood and time period. The dataset features `r x_neigh` unique Amsterdam neighborhoods and `r x_period` unique time periods (from Januray 2021 to December 2021 ). The table below highlights all of the columns available in the dataset along with their descriptions.

```{r table2, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
var_tab <- "
| Variable      | Description   | Data Class |
|---------------|:-------------:|----------:|
| neighborhood      | The respective neighborhood in Amsterdam to which the data pertains to. | Character |
| listing_sum      | The total amount of listings in the respective neighborhood. | Integer |
| average_price | The average price for listings in the respective neighborhood. | Integer |
| percentage_home_apt | The percentage of listings that are home apartments out of the amount of total listings. | Numeric |
| percentage_hotel_rool | The percentage of listings that are hotel rooms out of the amount of total listings. | Numeric |
| percentage_private_room | The percentage of listings that are private rooms out of the amount of total listings. | Numeric |
| percentage_shared_room | The percentage of listings that are shared rooms out of the amount of total listings. | Numeric |
| periods | The periods of time to which crime data pertains to. | Character |
| crime_type_category | The type of crime to which the data pertains to. | Character |
| total_crime_sum | The amount of crime occurances of a certain type in a certain period. | Integer |
"
cat(var_tab)
```


Based on the dataset, the area with the most amount of listings is `r n_m_l` with `r n_m_l_n` listings, while the area with the least is `r n_l_l` with `r n_l_l_n` listings. Furthermore, the most expensive area listings-wise is `r n_m_p` with `r n_m_p_n` average price, while the area with the least is `r n_l_p` with `r n_l_p_n` average price.

The graphs below visualize how the number of crimes has evolved throughout the available time periods, as well as the occurrences of crimes per type

```{r, crime-time, echo=FALSE}
df_crime_time = filter(listings_crime_dataset, crime_type_category == "Total") %>% group_by(periods) %>% summarise(total_crime = sum(total_crime_sum))
df_crime_time%>%
  ggplot(aes(x = periods, y = total_crime, group = 1)) + geom_point() + geom_path() +
  labs(x = "Periods (Month)", y = "Total Crime Cases" , title = "Total Crime Occurrences per Month") + 
  theme(axis.text.x=element_text(size = 8))

df_min_crime_time = df_crime_time[which.min(df_crime_time$total_crime),]
c_l_p = df_min_crime_time[1,1]
c_l_p_n = df_min_crime_time[1,2]
df_max_crime_time = df_crime_time[which.max(df_crime_time$total_crime),]
c_m_p = df_max_crime_time[1,1]
c_m_p_n = df_max_crime_time[1,2]
```
As it can be seen from the Crime Occurrences per Month graph, the data exhibits no seasonality trend when viewed on a 12 month period. The lowest number of crime occurrences is on `r c_l_p` with `r c_l_p_n` crimes, while the highest is on `r c_m_p` with `r c_m_p_n` crimes.  

```{r, crime-type-occur, echo=FALSE}
df_crime_type = filter(listings_crime_dataset, crime_type_category != "Total") %>% group_by(crime_type_category) %>% summarise(total_crime_sum = sum(total_crime_sum))
df_crime_type %>%
  ggplot(aes(x = crime_type_category, y = total_crime_sum, fill = crime_type_category)) + geom_bar(stat = 'identity') +
  labs(x = "Crime Type", y = "Crime Occurances", fill = "Crime Type", title = "Total Crime Occurances per Crime Category") +
  scale_fill_viridis_d() + theme(axis.text.x=element_text(size = 8))

df_min_crime_type = df_crime_type[which.min(df_crime_type$total_crime_sum),]
c_l_t = df_min_crime_type[1,1]
c_l_t_n = df_min_crime_type[1,2]
df_max_crime_type = df_crime_type[which.max(df_crime_type$total_crime_sum),]
c_m_t = df_max_crime_type[1,1]
c_m_t_n = df_max_crime_type[1,2]
```
When observing the distribution of Crime Occurrences per Crime Category graph, it is clear that crime occurrences are highly different in frequency. The graph clearly shows how the lowest number of crime occurrences is for `r c_l_t` crimes with `r c_l_t_n` occurrences, while the highest is `r c_m_t`  crimes with `r c_m_t_n` occurrences.

## Correlation Analysis

Before begging the analysis chapter, it is important to remember the hypothesis of this research:

*To what extent does the number of Airbnb listings affect crime rates within Amsterdam, and to what extent is this relationship different within different Amsterdam neighborhoods.*

To verify the validity of this hypothesis, the dataset will be used in a linear regression that takes the amount of crimes (total_crime_sum) as dependent variable, while taking the amount of listings(listings_sum) as independent variable and Amsterdam neighborhoods (neighborhood) as a categorical moderator. To make this possible the dataset has to be modified further - taking into account only the total crime figures (as in choosing only the rows where crime_type_category is "Total"). The regression formula used for this analysis is the following:

*total_crime_sum = listings_sum + neighborhood*

The following table shows the results of the regression analysis:

```{r, linear-regression, echo=FALSE}
regression_dataset <- listings_crime_dataset %>%
  filter(crime_type_category == "Total")


lr <- lm(total_crime_sum ~ listing_sum + neighborhood, data = listings_crime_dataset)

tidy(lr,conf.int = TRUE)
```
# The following indications show how this part should work: based on if statements, the Rmd should result in a pdf with the following outputs:

# If listings_sum is significant (<0.05):
Based on the regresion analysis, there is indeed correlation between the amount of listings and crime occurances, as the p coefficient of listing_sum is *insert p coefficient here*.

# If listings_sum is insignificant (>0.05):
Based on the regresion analysis, there is no correlation between the amount of listings and crime occurances, as the p coefficient of listing_sum is *insert p coefficient here*.

# If the amount of neighborhoods that are significant is =< 4: OR If the proportion of significant neighborhoods is =<20%:
The regression analysis indicates that a small number of Amsterdam neighborhoods have significantly different crime occurances. Only *insert name of significant neighborhoods here* are/is significant in this regresion. As *insert nr of sgnificant neighborohoods here* out of *insert total nr of neighborhoods here* have significant p coefficients, it is noticeable that the relationship between the number of listings and crime occurances is in large part unnafected by neighborhoods. 

# If the amount of neighborhoods that are significant is =< 10: OR If the proportion of significant neighborhoods is =<50:
The regression analysis indicates that some of Amsterdam neighborhoods have significantly different crime occurances. Thus, *insert name of significant neighborhoods here* are significant in this regresion. As *insert nr of sgnificant neighborohoods here* out of *insert total nr of neighborhoods here* have significant p coefficients, it is noticeable that the relationship between the number of listings and crime occurances is somewhat affected by neighborhoods. 

# If the amount of neighborhoods that are significant is =< 16: OR If the proportion of significant neighborhoods is =<80%:
The regression analysis indicates that most of Amsterdam neighborhoods have significantly different crime occurances. Thus, *insert name of significant neighborhoods here* are significant in this regresion. As *insert nr of sgnificant neighborohoods here* out of *insert total nr of neighborhoods here* have significant p coefficients, it is noticeable that the relationship between the number of listings and crime occurances is to a large extent affected by neighborhoods. 

# if R Squared is =< 0.5
Lastly, it is important to note that the R Squared of the correlation is *Insert R squared here*. Meaning that most of the variation exhibited in this dataset is not explained through this correlation model. 

# if R Squared is => 0.5
Lastly, it is important to note that the R Squared of the correlation is *Insert R squared here*. Meaning that most of the variation exhibited in this dataset is explained through this correlation model. 

## Conclusion
Based on the previous result section, the following conclusions can be drawn for the hypothesized relation:

# If both listings_sum is significant and most neighborhoods (=< 16 or 80%):
The hypothesis is accepted, as the correlational relationship between the amount of listings and crime occurances is significant, and the neighborhood moderatior value changes to a large extent their correlational nature.

# If both listings_sum is significant and some neighborhoods (=< 10 or 50%):
The hypothesis is accepted, as the correlational relationship between the amount of listings and crime occurances is significant, and the neighborhood moderatior value changes to some extent their correlational nature (although this may need to be explored further in a follow-up study).

# If both listings_sum is significant and a few neighborhoods (=< 4 or 20%):
The hypothesis is in part rejected, as the correlational relationship between the amount of listings and crime occurances is significant, while the neighborhood moderator value is largely displaying non-significant differences in their correlational nature.

# If both listings_sum is insignificant and most neighborhoods (=< 16 or 80%):
The hypothesis is in part rejected, as the correlational relationship between the amount of listings and crime occurances is insignificant, while the neighborhood moderatior value changes to a large extent their correlational nature.

# If both listings_sum is insignificant and some neighborhoods (=< 10 or 50%):
The hypothesis is rejected, as the correlational relationship between the amount of listings and crime occurances is insignificant, while the neighborhood moderatior value changes to some extent their correlational nature.

# If both listings_sum is insignificant and a few neighborhoods (=< 4 or 20%):
The hypothesis is rejected, as the correlational relationship between the amount of listings and crime occurances is insignificant, while the neighborhood moderatior value is largely displaying non-significant differences in their correlational nature.

# if R Squared is =< 0.5
Despite the result of the hypothesis, it is important to remember that *Insert R Squared value here as a percentage* of the variation exhibited in this dataset is explained through this correlation model. This means that these findings should be considered skeptically, as the data within the dataset may be insufficient to draw conclusions at this point. Enriching the dataset with more data and/or explanatory variables may result in more conclusive results.

# if R Squared is => 0.5
Regarding the validity of this hypothesis, it is important to remember that *Insert R Squared value here as a percentage* of the variation exhibited in this dataset is explained through this correlation model. This means that these findings benefit from a robust model and lends credence to them being correct. Nonetheless, it is important to consider that these findings may not be relevant to other geographical areas outside of Amsterdam, Netherlands. Just as well, the robustness of the model can be improved further through the addition of more relevant explanatory variables. 

## Sources

https://www.google.com/url?sa=t&rct=j&q=&esrc=s&source=web&cd=&ved=2ahUKEwjD_f2QuYn2AhUK7KQKHVp7Ap8QFnoECBUQAw&url=https%3A%2F%2Fczasopisma.uni.lodz.pl%2Ftourism%2Farticle%2Fdownload%2F2208%2F1864&usg=AOvVaw33IzV3UaT7bLLU_4VKm4kH

https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8691595/

https://www.statista.com/statistics/339845/company-value-and-equity-funding-of-airbnb/

https://www.theguardian.com/world/2018/jun/15/tourism-pollution-backlash-japan-crackdown-costs-airbnb-10m-kyoto
